%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Roy Dey} \\ \vspace{1pt}
    \small \href{https://roydey.com}{\underline{roydey.com}} $|$ \href{mailto:roydey10@gmail.com}{\underline{roydey10@gmail.com}} $|$ 
    \href{https://linkedin.com/in/roydey}{\underline{linkedin.com/in/roydey}} $|$
    \href{https://github.com/rdey0}{\underline{github.com/rdey0}}
\end{center}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, C++, ReScript, HTML, CSS, Go, SQL,} \\
     \textbf{Frameworks}{: React, Django, Graphene, GraphQL, GQLGen, Gorm, PostgreSQL, Bootstrap, AngularJS, NodeJS} \\
     \textbf{Developer Tools}{: Git, Docker, Amazon Web Server, Retool} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{March 2021 -- Sep. 2022}
      {SILQ}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Led implementation of purchase order system in Django, Graphene, and React to digitize itemized goods.}
        \resumeItem{Developed a quoting system using Django and Graphene to deliver accurate freighting quotes within 2 days, and replace the manual parsing and quote calculation of freighted goods.}
        \resumeItem{Built robust management UIs using React, allowing clients to monitor the progress of projects and shipments.}
        \resumeItem{Developed a React Native mobile app to improve efficiency of factory QA processes and simplify inspections.}
        \resumeItem{Built Internal dashboards and workflows using Retool to track critical metrics and record operations data.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Application Developer}{July 2019 -- June 2020}
      {University of California, Davis}{Davis, CA}
      \resumeItemListStart
        \resumeItem{Renovated UC Davis software ecommerce website to improve user experience and mobile support.}
        \resumeItem{Built testing platform using Angular, Bootstrap, and SQL, allowing university staff to create and administer tests with automated tools, saving 2+ hours of manual labor per week and replacing expensive vendor solutions.}
        \resumeItem{Developed robust search tools for staff to easily track software licenses, replacing manual spreadsheet lookup.}
        \resumeItem{Rapidly prototyped features to help university management determine future changes to web properties.}
    \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
              {\textbf{Restock Bot} $|$ \emph{NodeJS, JavaScript, Puppeteer}}{June 2020 -- Present}
              \resumeItemListStart
                \resumeItem{Developed a simple web scraping tool to send email notifications when desired items are restocked.}
                \resumeItem{Implemented asynchronous web scraping with Puppeteer}
                \resumeItem{Implemented email notification system with Nodemailer}
              \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Connect 4 AI} $|$ \emph{React, JavaScript}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a web application which pits players against an AI controlled opponent.}
            \resumeItem{Wrote AI algorithms}
            \resumeItem{Visualized GitHub data to show collaboration}
            \resumeItem{Used Celery and Redis for asynchronous tasks}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Raphunt} $|$ \emph{React, JavaScript, Reddit API}}{May 2018 -- May 2020}
          \resumeItemListStart
            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Davis}{Nov. 2016 -- June 2020}
      {Bachelor of Arts in Computer Science}{Davis, CA}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
